Let's Get Movin': Frontiers of Optimal Transport

### 2018-05-05 reports/paper/paper.tex
Modify intro to reflect Hungarian change of scope

The organization of this report is as follows: \cref{sub:problem_intro}
 introduces the
 discrete optimal transport problem and discusses its interpration, dual
 problem, and basic theoretical properties as a linear program. \cref{sec:exact} discusses methods to solve the optimal transport problem \eqref{eq:ot_problem}
 exactly, introducing the Hungarian algorithm \cite{kuhn2010hungarian} in 
\cref{sub:hungarian_algorithm} and presenting a proof of its correctness. The
 Hungarian algorithm is cubic in run-time, which is optimal for exact solution
 of \eqref{eq:ot_problem}, but is often too slow for practical
 applications discussed in \cref{sub:applications}. As such, we discuss
 approximate
 optimization methods in \cref{sec:inexact_methods}, where 
\cref{sub:entropic_regularization_and_sinkhorn_s_algorithm} focuses on the
 Sinkhorn-Knopp algorithm used to solve a convexification of 
\eqref{eq:ot_problem} known as \ref{eq:entropic}. We present an elegant and
 recent upper
 bound of Sinkhorn-Knopp's run-time by
 \cite{altschuler2017near}, as well as numerical experiments and speculations
 about future work. In \cref{sub:genetic_algorithms_}, we attempt to use genetic
 algorithms to approximately solve \eqref{eq:ot_problem}, motivated by recent advances by 
\cite{such2017deep}. In \cref{sec:applications_}, we showcase toy examples of
 using optimal transport in computer vision with the well-known MNIST dataset.
 \cref{sec:conclusion} concludes.

>>>>

The organization of this report is as follows: \cref{sub:problem_intro}
introduces the discrete optimal transport problem and discusses its
interpration, dual problem, and basic theoretical properties as a linear
program. \cref{sec:exact} discusses methods to solve the optimal transport
problem \eqref{eq:ot_problem} exactly, introducing the Hungarian algorithm
\cite{kuhn2010hungarian} in \cref{sub:hungarian_algorithm} and presenting an
empirical analysis of its runtime. The Hungarian algorithm appears cubic in
run-time, confirming theoretical asymptotic analysis, which is optimal for exact
solution of \eqref{eq:ot_problem}, but is often too slow for practical
applications discussed in \cref{sub:applications}. As such, we discuss
approximate optimization methods in \cref{sec:inexact_methods}, where
\cref{sub:entropic_regularization_and_sinkhorn_s_algorithm} focuses on the
Sinkhorn-Knopp algorithm used to solve a convexification of
\eqref{eq:ot_problem} known as \ref{eq:entropic}. We present an elegant and
recent upper bound of Sinkhorn-Knopp's run-time by \cite{altschuler2017near}, as
well as numerical experiments and speculations about future work. In
\cref{sub:genetic_algorithms_}, we attempt to use genetic algorithms to
approximately solve \eqref{eq:ot_problem}, motivated by recent advances by
\cite{such2017deep}. In \cref{sec:applications_}, we showcase toy examples of
using optimal transport in computer vision with the well-known MNIST dataset.
\cref{sec:conclusion} concludes.
